Thomas et al. 2025

### 2025-07-23 IndividualStudies/AT_2025.qmd
working on uploading Franks new analysis of Alixs data. Working in new branch.

>>>>

## NB: This is a test page with the re-analyzed data from Frank

I see from this new analysis that the publication only included the results from the membrane prep -- and excluded the cytosol fraction. Just because Frank provided both sets in his re-worked analysis, I wanted to incorporate both here to see if we want to display both online; if we decide we don't want the cytosol prep, I can easily remove that section!

### 2025-07-23 IndividualStudies/AT_2025_2.qmd
working on uploading Franks new analysis of Alixs data. Working in new branch.

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
date: 2024-12-26
format: 
  html:
    embed-resources: false
standalone: false
---
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

@@

## Data visualization

@@

## intitialize libraries
library(here)

@@

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
# Read the data to a df

data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

@@

print("Data not yet provided.")

@@

:::
:::

## Gene Ontology Analysis

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
:::::

## Data exploration

@@

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 20))

@@

## Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_download.csv dname="AT_ChemicalCommunications_2025">}}

>>>>

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
date: 2024-12-26
format: 
  html:
    embed-resources: true
standalone: true
---
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

@@

::: {.callout-tip}

## Membrane Fraction

### Data visualization

@@

## intitialize libraries
library(here)
library(dplyr)
library(duckplyr)
library(ggplot2)
library(ggrepel)
library(emojifont)
library(dplyr)
library(tidyr)
library(docstring)
library(clusterProfiler)
library(org.Hs.eg.db)
library(enrichplot)
library(igraph)
library(ggtangle)
library(stringr)
library(crosstalk)
library(plotly)
library(grid)
library(readr)
library(rmarkdown)
library(gt)
library(DT)
library(heatmaply)
library(ggvenn)
library(scales)
library(htmltools)

@@

# Read the membrane data to a df
data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_membrane_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

data |>
  arrange(hit_annotation) |>
  glimpse()

@@

MAStandard(data)

@@

:::
:::
<!-- 
### Gene Ontology Analysis

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
::::: -->

### Data exploration

@@

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 10))

@@

### Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_membrane_download.csv dname="AT_ChemicalCommunications_2025">}}

:::{.callout-tip}

## Cytosolic Fraction

### Data visualization

```{r setup2, echo=FALSE, include=FALSE}

## intitialize libraries
library(here)
library(dplyr)
library(duckplyr)
library(ggplot2)
library(ggrepel)
library(emojifont)
library(dplyr)
library(tidyr)
library(docstring)
library(clusterProfiler)
library(org.Hs.eg.db)
library(enrichplot)
library(igraph)
library(ggtangle)
library(stringr)
library(crosstalk)
library(plotly)
library(grid)
library(readr)
library(rmarkdown)
library(gt)
library(DT)
library(heatmaply)
library(ggvenn)
library(scales)
library(htmltools)

# Read the membrane data to a df
data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_Cytosol_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

data |>
  arrange(hit_annotation) |>
  glimpse()

MAStandard(data)

:::
:::
<!-- 
### Gene Ontology Analysis

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
::::: -->

### Data exploration

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 10))

### Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_cytosol_download.csv dname="AT_ChemicalCommunications_2025">}}
